Tropical mathematics for the Lambda-calculus 1

### 2023-07-29 CSL24/section5.tex
Commit ancora più sonnolento
Chiarito

\begin{remark}\label{rmk:tropof01Rel}
$\model{M}^{\LREL}_0(-\log p,-\log (1-p))$ gives the minimum negative log-probability of all the reductions from $M$ to normal form, i.e.\ it coincides with the  negative log-probability of any of the (equiprobable) \emph{most} likely reductions from $M$ to normal form.
Equivalently, given $\omega_0$ a fixed reduction path from $M$ to normal form $P_{\omega_0}$, for all solution $p\in[0,1]$ to the equation $%\trop P_\omega(-\log p, -\log(1-p)) 
-\log  P_{\omega_0} = \model{M}^{\LREL}_0(-\log p,-\log (1-p))$, the path $\omega_0$ is one of the \emph{most} likely one among all paths from $M$ to normal form.
Similarly, $\model{M}^{\LREL}_0(\log p,\log (1-p))$ gives the minimum log-probability of all the reductions from $M$ to normal form, i.e.\ it coincides with the log-probability of any of the (equiprobable) \emph{less} likely reductions from $M$ to normal form.
Equivalently, given $\omega_0$ a fixed reduction path from $M$ to normal form $P_{\omega_0}$, for all solution $p\in[0,1]$ to the equation $%\trop P_\omega(\log p, \log(1-p)) 
\log  P_{\omega_0} = \model{M}^{\LREL}_0(\log p,\log (1-p))$, the path $\omega_0$ is one of the \emph{less} likely one among all paths from $M$ to normal form.
% (in $p$ and $q$, not after the substitution $q:=r-p$) 
% are extracted from it, \ref{eq:argmax}, \ref{eq:max} of $\STLC_\oplus$-programs. 
\end{remark}

>>>>

\begin{remark}\label{rmk:tropof01Rel}
$\model{M}^{\LREL}_0(-\log p,-\log (1-p))$ gives the minimum negative log-probability of all the reductions from $M$ to $\false$, i.e.\ it coincides with the  negative log-probability of any of the (equiprobable) \emph{most} likely reductions from $M$ to $\false$.
Equivalently, given $\omega_0$ a fixed reduction path from $M$ to $\false_{\omega_0}$, for all solution $p\in[0,1]$ to the equation $%\trop P_\omega(-\log p, -\log(1-p)) 
-\log  P_{\omega_0} = \model{M}^{\LREL}_0(-\log p,-\log (1-p))$, the path $\omega_0$ is one of the \emph{most} likely one among all paths from $M$ to $\false$.
Similarly, $\model{M}^{\LREL}_0(\log p,\log (1-p))$ gives the minimum log-probability of all the reductions from $M$ to $\false$, i.e.\ it coincides with the log-probability of any of the (equiprobable) \emph{less} likely reductions from $M$ to $\false$.
Equivalently, given $\omega_0$ a fixed reduction path from $M$ to $\false_{\omega_0}$, for all solution $p\in[0,1]$ to the equation $%\trop P_\omega(\log p, \log(1-p)) 
\log  P_{\omega_0} = \model{M}^{\LREL}_0(\log p,\log (1-p))$, the path $\omega_0$ is one of the \emph{less} likely one among all paths from $M$ to $\false$.
% (in $p$ and $q$, not after the substitution $q:=r-p$) 
% are extracted from it, \ref{eq:argmax}, \ref{eq:max} of $\STLC_\oplus$-programs. 
\end{remark}
